Visualizing Project Evolution Through Abstract Syntax Tree Analysis

### 2016-04-09 paper/paper.tex
Update tex.

@@

@@

For example, in December of 2011 we can see that the ParserATNSimulator class has a large amount of additions and deletions in roughly equal proportion (Figure~\ref{fig:parser1}. This suggests that ParserATNSimulator is not being removed from the project but instead there is some refactoring being done. If we take a closer look at the commit messages we can see that they mention refactoring and reorganization of code (Figure~\ref{fig:parser2}). Zooming in on that date,  shows that during that month they were finishing work on a new version of ParserATNSimulator.

@@

>>>>

\begin{figure*}[!t]
\centering
\includegraphics[width=\textwidth]{antlr-3-code-freq-edit}
\caption{}
\end{figure*}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]{ParserATNSimulator}
\caption{}
\label{fig:parser1}
\end{figure}

@@

For example, in December of 2011 we can see that the ParserATNSimulator class has a large amount of additions and deletions in roughly equal proportion (Figure~\ref{fig:parser1}). This suggests that ParserATNSimulator is not being removed from the project but instead there is some refactoring being done. If we take a closer look at the commit messages we can see that they mention refactoring and reorganization of code (Figure~\ref{fig:parser2}). Zooming in on that date,  shows that during that month they were finishing work on a new version of ParserATNSimulator.

@@

\begin{figure}[!h]
\centering
\includegraphics[width=\columnwidth]{antlr-density}
\caption{}
\end{figure}

\begin{figure}[!h]
\centering
\includegraphics[width=\columnwidth]{tika-density}
\caption{}
\end{figure}
